\plaintitle

### 2016-08-20 drafts/labor/cases.tex
friday edits, mostly rearranging, some additions

\subsubsection{Achieving greater complexity}\label{sec:Complexity}
\topic{Crowdsourcing research has spent the better part of a decade attempting
to prove the viability of crowdsourcing in increasingly complex work.}  % this is my topic sentence.
\citeauthor{crowdForgeKittur}
map the discussion toward this goal in their work on
crowdsourcing complex work
\cite{crowdForgeKittur}.
\citeauthor{Lasecki:2013:CCC:2501988.2502057} tackle an area of computationally assisted interaction
--- conversational artificial intelligence ---
and find ways to arrange workers and formulate a ``crowd--powered conversational assistant''
\cite{Lasecki:2013:CCC:2501988.2502057}.
Other work has followed a similar pattern,
identifying target milestones in Computer Science
that have presented significant challenges for researchers,
and demonstrating that ``crowd--powered'' systems can tackle many of these challenges
with generally greater success than purely computational attempts
\cite[][and others]{Lasecki:2013:RCL:2441776.2441912,foundry}.

\topic{While much of the above work has focused on
clever arrangements of systems to manage collectives of workers,
another body of work has turned inward toward managing the self.}
\citeauthor{selfsourcingTeevan2014} push the boundaries of decomposed work,
exploring ``selfsourcing'', and further this work with \citeauthor{selfsourcingTeevan2016}
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016}.
While some of this work doesn't strictly fall under ``crowdsourcing'',
the [scientific] management of the self as a worker
(of sorts)
will prove relevant as we trace the literature surrounding piecework.

\topic{A smaller but growing body of work has reflected on this
and brought to our attention a number of ethical questions surrounding the
increasing complexity of crowdwork and the hazards that increasingly arise.}
\citeauthor{professionalCrowdworkEthics} bring some of these issues at stake
--- working for increasing amounts of time on tasks of growing complexity, only to discover that requesters are not willing to pay,
for instance ---
but these and other dangers range an enormous landscape % too informal?
\cite{crowdworkFuture,professionalCrowdworkEthics,nickerson2013crowd,dynamo}.

\topic{We summarize the work discussed so far in this way:
researchers of crowdsourcing and on--demand labor in general
have attempted to find the characteristics which
enable and stymie successful applications of this form of work,
and how to get past or around these boundaries.}
Whether this work has focused on the self (as in the case of ``selfsourcing'')
or on others (as in \textit{CrowdForge} and \textit{Foundry}),
crowdsourcing literature has generally studied the constituent work
and attempted either to work around or indeed with the limitations of crowdwork to accomplish a difficult task
\cite{selfsourcingTeevan2014,selfsourcingTeevan2016,crowdForgeKittur,foundry}.

% \topic{Research into piecework has also explored the limits of piecework,
% with some findings.}

\ali{

Talked to someone about this section and got some feedback\dots
\begin{enumerate}
  \item Explain what ``clever arrangement of work'' in the first paragraph means
        (should be simple; Find--Fix--Verify is the \textit{sort} of thing I mean);
  \item I should make the ``selfsourcing'' stuff clearer for people unfamiliar with it
        (maybe even to justify its placement here); and
  \item I should break up \citeauthor{10.2307/23702539} \& \citeauthor{Brown01041990}
        to make the historical stuff on piecework
        directly speak to the three previous paragraphs.
  \item (Maybe?) summarize the piecework stuff
        (the last paragraph approaches that, but more could be done).
\end{enumerate}
Thoughts on this?

}

% the language used to describe the factors considered for piecework to thrive.}
First, we look to
\citeauthor{10.2307/23702539},
who describes piecework as
    ``\dots~based on examination of various shop jobs,
    which included calculation of the standard time and compensation for each task''
\cite{10.2307/23702539}.
\citeauthor{10.2307/23702539} later enumerates some of the roles required
to facilitate piecework in the early \nth{20} century:
    ``\dots~piecework clerks, inspectors, and ``experts''\dots''
\cite{10.2307/23702539}.
\citeauthor{Brown01041990} makes a more assertive
claim about the factors necessary for piecework to thrive,
specifically arguing that
    ``\dots~incentive pay is less likely in jobs with
    a variety of duties than in jobs with a narrow set of routinized duties''
\cite{Brown01041990}.
\citeauthor{10.2307/23702539} makes another claim that
successful cases of piecework owed themselves in part to the fact that
    ``\dots~only [the largest and most wealthy railroads] had the resources to~\dots
    pay the overhead involved in installing work reorganization''
\cite{10.2307/23702539}.

\topic{Digital media have expanded the scope of viable piecework by pushing drastically on the limits
cited by piecework researchers.}
The research on piecework tells us that
we should expect piecework to thrive in industries where
the nature of the work is limited in complexity.
Given the flourishing of on--demand labor platforms such as
Uber, Amazon Mechanical Turk, and others, we ask ourselves
what --- if anything --- has changed.
We argue that the Internet has trivialized the costs and challenges of the earlier limiting factors for two reasons:
\begin{inlinelist}
  \item Technology make it much easier to do complex work aided by computers; and % is there a source for this? Is this necessary to cite?
  \item The Internet allows us to leverage the benefits of ``economies of scale'' at very little cost
        to the system--designer \cite{lessig2006code}
\end{inlinelist}.

\ali{\citeauthor{10.2307/23702539} also argues that
a significant obstacle to the introduction of piecework in railroad shops was
the resistance of workers
(the other being the resistance of management (for different and varying reasons)).
In the cases of online platforms like AMT and digitally mediated platforms like Uber,
where in both cases workers rarely
if ever
interact face--to--face and
opportunities for coordination and collective action are severely limited,
we should expect to see
the challenges stymieing collective action
that we see in \citeauthor{dynamo} and elsewhere
\cite{10.2307/23702539,dynamo}.}

@@

\citeauthor{embracingErrorKrishna} take a different approach;
by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds,
the authors offer orders--of--magnitude improvements
in various binary classification tasks
% on the principle that diverse workers complete these tasks
% in order to accurately inform the model on the variety of delays in response times.
\cite{embracingErrorKrishna}.
And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
some researchers have designed work predicated on the expectation of it instead:
\citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
crowd workers would never be given enough information to piece together sensitive information about
any single topic
\cite{sensitiveTasks}.

@@

% \subsubsection{Piecework's role here}
% We address the question of the limits of crowdsourcing in three parts:
% \begin{inlinelist}
% \item decomposition
% \item work abstraction
% and \item flexibility
% \end{inlinelist}.
% The literature on piecework has offered insights into each of these topics, which we will explore now.

@@

\citeauthor{cheng2015break} found that microtasks
--- though not necessarily \textit{faster} than ``macrotasks'' ---
yield higher quality work,
particularly when that work is susceptible to frequent interruptions
\cite{cheng2015break}.

@@

    % Low pay yields variable quality work for a number of reasons,
    % but before we discuss the causes of this effect, we should discuss the

    % Variance in the quali

@@

  \end{appendices}
  }

>>>>

\subfile{complexity}

@@

\citeauthor{embracingErrorKrishna} take a different approach;
by ``embracing error'' and forming models describing the latency of workers in classifying objects at rapid speeds,
the authors offer orders--of--magnitude improvements
in various binary classification tasks
\cite{embracingErrorKrishna}.
And rather than building tasks to \textit{tolerate} worker drop--off and attrition,
some researchers have designed work predicated on the expectation of it instead:
\citeauthor{sensitiveTasks} describe ways of assigning tasks in such a way that
crowd workers would never be given enough information to piece together sensitive information about
any single topic
\cite{sensitiveTasks}.

@@

@@

\endnotetext{
    \citeauthor{cheng2015break} found that microtasks
    --- though not necessarily \textit{faster} than ``macrotasks'' ---
    yield higher quality work,
    particularly when that work is susceptible to frequent interruptions
    \cite{cheng2015break}.
}

@@

@@

  \theendnotes
  \end{appendices}
  }
